### 2017-04-15 paper/evaluation.tex
pass on rq5 (after Luis' pass)

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
%\end{figure}
\end{wrapfigure}

@@

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

\begin{enumerate}
\item How long does it take for test to run in your environment? Can
  you briefly define your setup?
\item Do you confirm that your project does not run in parallel?
\item\label{questionThree} Select a reason for not using parallelization:
  \begin{enumerate}[label=\alph*)]
  \item I did not know it was possible
  \item I was concerned with concurrency issues
  \item I use a continuous integration server
  \item Some other reason. Please elaborate.
  \end{enumerate}
\end{enumerate}

@@

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites were modularized and
those modules are tested independetly in CI servers through different
parameters. A total of \emailsLocal{} participants answered that they
do run tests in their local machines.  Note, however, that CI does not
preclude low-level parallelization.  For example, installations of
open-source CI tools (\eg{}, Jenkins~\cite{jenkins}) in dedicated
servers will still benefit from running tests faster through low-level
test suite parallelization.

@@

Considering question 2, the answers we collected show that six of the
\emailsProjectsAnswered{} projects execute tests in parallel.  This
mismatch is justified by cases where neither of our checks (static or
dynamic) could detect presence of parallelism.  A closer look at these
projects revealed that one of them contained a \emph{pom.xml} file
encapsulated in a jar file (similar case as reported in
Section~\ref{sec:rqC-2}), in one of the projects the particpant
considered that distributed CI was a form of parallelism, and in four
projects parallelism was implemented natively\Luis{$\leftarrow$ is
this the right word?}~---~two projects
implemented concurrency control with custom JUnit test runners and two
other projects implemented concurrency within test methods.  Note
that, considering four extra cases (ignored two distributed CI cases),
the usage of parallelization increases from \percentParallel{} to
\percentParallelUpdated{}.  However, we do not consider this change
significant enough to modify our conclusion about practical adoption
of parallelization (\numRQC{}).

@@

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
the distribution of answers.

>>>>

@@

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{wrapfigure}
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

\begin{enumerate}
\item How long does it take for tests to run in your environment? Can
  you briefly define your setup?
\item Do you confirm that your regression test suite does *not* run in parallel?
\item\label{questionThree} Select a reason for not using parallelization:
  \begin{enumerate}[label=\alph*)]
  \item I did not know it was possible
  \item I was concerned with concurrency issues
  \item I use a continuous integration server
  \item Some other reason. Please elaborate.
  \end{enumerate}
\end{enumerate}

@@

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites are modularized and
those modules are tested independetly in CI servers through different
parameters.  Those participants argumented that such practice helps to
reduce time to observe test failures, which is the goal of speeding up
regression testing.  A total of \emailsLocal{} participants answered
that they do run tests in their local machines.  Note, however, that
CI does not preclude low-level parallelization.  For example,
installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
in dedicated servers would benefit from running tests faster through
low-level test suite parallelization.

@@

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the particpant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQC{}).

@@

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
the distribution of answers.
